---
title: "Weekly Option Data Integrity Test"
subtitle: "SPY: 2014-2018"
author: "Pritam Dalal"
output: 
  html_document:
    df_print: paged  
editor_options: 
  chunk_output_type: console
---


<style>
    body .main-container {
        max-width: 700px;
    }
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = TRUE
    #, comment = "#>"
    #, collapse = TRUE
)

options(width = 100)
```


```{r, loading_packages, include=FALSE, cache=TRUE}
######################
## loading packages ##
######################
library(tidyverse)
library(lubridate)
library(tidyquant)
library(bizdays)


# initializing bizdays libraries
load_rmetrics_calendars(2000:2020)
bizdays.options$set(default.calendar="Rmetrics/NYSE")
```


```{r, reading_data, include=FALSE, cache=TRUE}
#####################
## reading in data ##
#####################
df_chain_desc <- 
    read_csv("data_output/spy_weekly_2014_2018_chain_desc.csv")

df_chain_hist <-
    read_csv("data_output/spy_weekly_2014_2018_chain_hist.csv")

df_opt_hist <- 
    read_csv("data_output/spy_weekly_2014_2018_opt_hist.csv")

df_pnl <- 
    read_csv("data_output/spy_weekly_2014_2018_pnl_master.csv")

df_trade <- 
    read_csv("data_output/spy_weekly_2014_2018_trade_master.csv")

```




```{r, additional_data, include=FALSE, cache=TRUE}
#####################
## all trade dates ##
#####################
df_td_all <- 
    tibble(
        trade_date = bizseq(from = "2014-01-03", to = "2018-12-29")
    )

#dt_all <- bizseq(ymd(20140103), ymd(20181229))
#df_td_all <- tibble(trade_date = dt_all)

###################################################
## grabbing price data from yahoo with tidyquant ##
###################################################
df_underlying_px <- 
    tq_get("SPY", from = "2014-01-03", to = "2018-12-29")

########################################################
## grabbing volatility index from FRED with tidyquant ##
########################################################
# df_vol_index <-
#     tq_get(
#         "VIXCLS"
#         , get = "economic.data"
#         , from = "2014-01-03"
#         , to = "2018-12-29"
#     )

df_vol_index <- 
    read_csv("data_input/vix9ddailyprices.csv")

df_vol_index$Date <- mdy(df_vol_index$Date)
```

<br>

### Dates with Missing Data
These queries perform a crude check: *Are there any trade dates with completely missing data?*  If so, it could mean that there is something seriously wrong in the wrangling, process.


#### **`df_chain_hist`**
```{r, dates_missing_data_chain_hist, cache=TRUE}

# df_chain_hist 
df_td_all %>%
    left_join(
        df_chain_hist
        , by = "trade_date"
    ) %>%
    filter(is.na(underlying))


```


#### **`df_opt_hist`**
```{r, dates_missing_data_opt_hist, cache=TRUE}
# df_opt_hist
df_td_all %>%
    left_join(
        df_opt_hist
        , by = c("trade_date" = "data_date")
    ) %>%
    filter(is.na(underlying_symbol))
```

<br>

### Underlying Price Differences
One of the major driverw of PNL in my backtests is the underlying prices.  In particular, I used them directly to calculate the final payoff of the options.  I check the values in the delta-neutral data set against Yahoo prices by using the `tidyquant` package. 


Currently, it tests for difference of greater than 0.25%, but of course this sensitivity could be changed.

```{r, upx_differences, cache=TRUE}
df_underlying_px %>% 
    select(date, close) %>% 
    left_join(
        df_opt_hist %>% select(data_date, underlying_price)
        , by = c("date" = "data_date")
    ) %>% 
    filter(abs((close - underlying_price) / close) > 0.0025) %>% 
    group_by(date) %>% 
    summarize(
        close = mean(close)
        , underlying_price = mean(underlying_price)
    ) %>% 
    mutate(
        diff = close - underlying_price
    ) 
```


<br>

### Missing Option Histories
Each unique option should have `n + 1` rows in `df_opt_hist` where `n` is the `d2x` of the option on execution date.  (Note: the reworking of the `missing_data()` function that I did on 2/28/2019 is what makes this hold in a strong way.)
```{r, missing_option_prices, cache=TRUE}
df_opt_hist %>% 
    group_by(
        underlying_symbol, type, expiration, strike
    ) %>% 
    summarize(
        row_count = n()
    ) %>%
    left_join(
        df_chain_desc %>% select(expiration, d2x)
        , by = "expiration"
    ) %>% 
    filter(row_count != (d2x + 1))
```

<br>

### Basic Checks on `df_chain_desc`
These are some basic checks on `df_chain_desc` that check for major problems with the wrangling process.  They also chec that the underlying is tradeable for each expriation.
```{r, basic_chain_desc, cache=TRUE}
# 1) make sure there are no chains with less than four days to expiration
df_chain_desc %>% 
    filter(d2x < 4)


# 2) make sure there are at least 6 options per chain
df_chain_desc %>% 
    filter(num_opts < 6)

# 3) make sure exec_day_volume is greater than 1000
df_chain_desc %>% 
    filter(exec_day_volume < 1000)

```

<br>

### Implied Volatilities vs Lagged Realized
There are two major components of expiration level PNL, the option prices on expiration date, the deltas (which I have no real cause for concern over), and the underlying prices used to calculate the delta-hedging.

In this section we start to look at the implied volatilities.


```{r, graphing_bid_ivs, cache=TRUE}
# this is the graph of execution date bid swap rates
# it's a good visual to look at, but it's hard to garner much
# data integrity
df_chain_hist %>%
    left_join(
        df_chain_desc %>% select(expiration, execution, realized_vol)
        , by = "expiration"
    ) %>%
    filter(trade_date == execution) %>%
    ggplot() +
        geom_line(aes(x=trade_date, y=bid_swap_rate), color="red") +
        geom_line(aes(x=trade_date, y=realized_vol), color="blue")
```



The next bit of analysis captures this essential feature of volatility markets: there should be a spike in realized volatility, immeditaly after there


```{r, cache=TRUE}
# lining up realized volatility and implied volatility by expiration
df_real_iv_comparison <-
    df_chain_hist %>%
    left_join(
        df_chain_desc %>%
            select(expiration, execution, realized_vol, return)
        , by = "expiration"
    ) %>%
    filter(trade_date == execution) %>%
    select(
        expiration, execution, bid_swap_rate, realized_vol, return
    ) %>%
    mutate(
        realized_change = realized_vol - lag(realized_vol)
        , iv_change = bid_swap_rate - lag(bid_swap_rate)
    )


# looking at the subsequent change in vol for each expiration
df_real_iv_comparison <-
    df_real_iv_comparison %>%
        mutate(
            subseq_iv_change = lead(iv_change)
        )


# There shouldn't be too many of these:
# (1) a sizeable jump in realized vol (> 5%)
# (2) the underlying experienced a loss during the expiration (< 0%)
# (3) a sizeable drop in implied vol (< -2%)
df_real_iv_comparison %>%
    filter(realized_change > 0.05) %>%
    filter(return < 0) %>%
    filter(subseq_iv_change < -0.02)
```


<br>

### Implied Volatility vs CBOE Volatility Index
In the previous section we compared implieds to realized.  Now we are comparing our implied to a volatility index.


```{r, bid_iv_vs_vol_index, cache=TRUE}
###############################################################
## checking the bid-IVs are consistent with volatility index ##
###############################################################
df_index_comparison <-
    df_chain_hist %>%
        select(underlying, expiration, trade_date, bid_swap_rate) %>%
        left_join(
            df_chain_desc %>%
                select(expiration, execution, realized_vol, return)
            , by = "expiration"
        ) %>%
        filter(trade_date == execution) %>%
        left_join(
            df_vol_index %>%
                mutate(vol_index = Close / 100) %>%
                select(Date, vol_index)
            , by = c("trade_date" = "Date")
        )


# calculating the difference between the bid swap rate and the vol_index
df_index_comparison <-
    df_index_comparison %>%
        mutate(vol_diff = bid_swap_rate - vol_index)

# difference between bid_swap_rate and vol_index is greater than 0.05
df_index_comparison %>%
    filter(abs(vol_diff) > 0.05)
```

<br>

### Delta-Hedge PNLs vs Realized Volatility Premium

The delta-hedged strangle PNLs should be a function of the realized volatility premium.  In this section, we check that this is the case.

```{r, pnl_vs_vol_prem, cache=TRUE, include=FALSE}
# premium by expiration
df_prem_exp <-
    df_trade %>%
        filter(variation == 0.1) %>%
        group_by(
            underlying_symbol
            , expiration
        ) %>%
        summarize(
            premium = sum(bid)
        )


# pnl by expiration
df_pnl_exp <-
    df_pnl %>%
        filter(variation == 0.1) %>%
        group_by(
            underlying_symbol
            , expiration
        ) %>%
        summarize(
            pnl = sum(dly_tot_pnl)
        )


# premium recieved and dh pnl for each expiration
df_prem_vs_pnl <-
    df_prem_exp %>%
        left_join(
            df_pnl_exp
            , by = c("underlying_symbol", "expiration")
        )



# for each expiration, the bid swap rate and the realized vol
df_vol_prem <-
    df_chain_desc %>%
        select(underlying, expiration, execution, realized_vol) %>%
        left_join(
            df_chain_hist %>%
                select(underlying, expiration, trade_date, bid_swap_rate)
            , by = c("underlying", "expiration")
        ) %>%
        filter(trade_date == execution) %>%
        select(underlying, expiration, realized_vol, bid_swap_rate) %>%
        mutate(
            vol_prem = bid_swap_rate - realized_vol
        )


# a final report that puts together all the numbers that we are
# interested in
df_report <-
    df_prem_vs_pnl %>%
        left_join(
            df_vol_prem
            , by = c("underlying_symbol" = "underlying", "expiration")
        ) %>%
        mutate(
            pnl_ratio = pnl / premium
        )

```


Let's begin look at a scatter plot of the vol-premium vs PNL ratio.

```{r, scatter_vol_prem_vs_pnl, cache=TRUE}
# scatter plot of vol-premium vs PNL ratio
df_report %>%
    ggplot() +
    geom_point(aes(x = vol_prem, y = pnl_ratio))
```

#### PNLs Directionally Correct
Let's count how many of the expiration PNLs were directionally correct.  This should be a high percentage.
```{r, directionally_correct_cases, cache=TRUE}
df_report %>%
    filter(
        (vol_prem > 0 & pnl_ratio > 0) |
        (vol_prem < 0 & pnl_ratio < 0)
    ) %>% 
    head(5)
```


#### Should Be Winners
Let's see how many should have been winners but actually turned out to be losers.


```{r, should_be_winners, cache=TRUE}
# should have been winners but they were losers
df_report %>%
    filter(vol_prem > 0 & pnl_ratio < 0) %>%
    arrange(pnl_ratio)
```


```{r, worst_should_be_winner_date, cache=TRUE, inclue=FALSE}
dt_worst_should_be_winner <- 
    df_report %>%
        filter(vol_prem > 0 & pnl_ratio < 0) %>%
        top_n(-1, pnl_ratio) %>% 
        .$expiration %>% 
        `[`(1)
```


We explore the most egregious case and make sure the that we agree with the numbers.

```{r, worst_should_be_winner_pnl, cache=TRUE, echo=FALSE}
df_pnl %>%
    filter(variation == 0.1) %>%
    filter(expiration == dt_worst_should_be_winner) %>% 
    select(
        underlying = underlying_symbol, expiration, data_date
        , type, strike, bid, ask, upx = underlying_price
        , delta, dly_opt_pnl, dly_dh_pnl, dly_tot_pnl  
    )
```


```{r, worst_should_be_winner_realized_vol, cache=TRUE}
# looking at one particular case and confirming that I
# agree with the numbers
df_pnl %>%
    filter(variation == 0.1) %>%
    filter(expiration == dt_worst_should_be_winner) %>%
    filter(type == "call") %>%
    select(underlying_price) %>%
    mutate(
        ret = log(underlying_price) - log(lag(underlying_price))
    ) %>%
    .$ret %>% sd(na.rm = TRUE) * sqrt(252)
```

#### Should Be Losers



```{r, should_be_losers, cache=TRUE}
# should have been losers but they were winners (34 of 260)
df_report %>%
    filter(vol_prem < 0 & pnl_ratio > 0) %>%
    arrange(desc(pnl_ratio))
```



```{r, worst_should_be_loser_date, cache=TRUE, echo=FALSE}
dt_worst_should_be_loser <- 
    df_report %>%
        filter(vol_prem < 0 & pnl_ratio > 0) %>%
        top_n(-1, pnl_ratio) %>% 
        .$expiration %>% 
        `[`(1)
```

We explore the most egregious case and make sure the that we agree with the numbers.

```{r, worst_should_be_loser_pnl, cache=TRUE, echo=FALSE}
df_pnl %>%
    filter(variation == 0.1) %>%
    filter(expiration == dt_worst_should_be_winner) %>% 
    select(
        underlying = underlying_symbol, expiration, data_date
        , type, strike, bid, ask, upx = underlying_price
        , delta, dly_opt_pnl, dly_dh_pnl, dly_tot_pnl  
    )
```

















