---
title: "2014-2018: Delta-Variation"
author: "Pritam Dalal"
date: "March 11, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

<style>
    body .main-container {
        max-width: 700px;
    }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, load_packages, include=FALSE}
library(tidyverse)
```

```{r, reading_monthly_data, include=FALSE, cache=TRUE}
chr_csv_file_names <-
        list.files(
            "data_output/monthly"
            , full.names = TRUE
            , pattern = ".*_pnl_scaled.csv*"
        )

lst_monthly <- list()
for (ix in 1:length(chr_csv_file_names)){
    lst_monthly[[length(lst_monthly) + 1]] <- 
        read_csv(chr_csv_file_names[ix], col_types = cols())
}

df_monthly <- bind_rows(lst_monthly)
df_monthly <-
    df_monthly %>% mutate(tenor = "monthly")
```



```{r, reading_weekly_data, include=FALSE, cache=TRUE}
chr_csv_file_names <-
        list.files(
            "data_output/weekly"
            , full.names = TRUE
            , pattern = ".*_pnl_scaled.csv*"
        ) 

lst_weekly <- list()
for (ix in 1:length(chr_csv_file_names)){
    lst_weekly[[length(lst_weekly) + 1]] <- 
        read_csv(chr_csv_file_names[ix], col_types = cols())
}

df_weekly <- bind_rows(lst_weekly)

df_weekly <- 
    df_weekly %>% mutate(tenor = "weekly")
```




```{r, combinind_monthly_weekly_pnls, include=FALSE, cache=TRUE}
df_pnl <- bind_rows(df_monthly, df_weekly)
```


```{r, daily_ttd_pnl, include=FALSE, cache=TRUE}
df_pnl_daily <- 
    df_pnl %>% 
        group_by(tenor, underlying_symbol, variation, data_date) %>% 
        summarize(
            naked = sum(scaled_dly_opt_pnl)
            , dh = sum(scaled_dly_tot_pnl)
        ) %>% 
        mutate(
            ttd_naked = cumsum(naked)
            , ttd_dh = cumsum(dh)
        )
```


```{r, calc_sharpe, include=FALSE, cache=TRUE}
df_sharpe <- 
    df_pnl_daily %>% rename(underlying = underlying_symbol) %>% 
        group_by(tenor, underlying, variation) %>% 
        summarize(
            avg_naked = mean(naked)
            , avg_dh = mean(dh)
            , sd_naked = sd(naked)
            , sd_dh = sd(dh)
            , sharpe_naked = (mean(naked) / sd(naked)) * sqrt(252)
            , sharpe_dh = (mean(dh) / sd(dh)) * sqrt(252)
            
        )

# removed the groupings
df_sharpe <-
    ungroup(df_sharpe)
```



In my previous research, the evidence suggests that selling 10-delta strangles out performs selling 30-delta strangles, and selling 50-delta strangles.

In this analysis, we attempt to corroborate or refute these results.



### Underlying/Tenor Combinations Indiviudally
In this section we consider underlying/tenor cominations individually, and check to see how often the sharpe ratio of 10-delta variation is higher than the 30-delta and 50-delta.

However, as with the Monthly vs Weekly analysis, some of the underlying/variation/tenor combinations have negative returns, and hence a negative sharpe, so we can't use sharpe to rank all strategies.

There are two work around to this:

1. Limiting the analysis to underlying/variation combinations where both tenors have a positive sharpe ratio.

2. Using the rank-sharpe ratio to compare the tenors (wasn't able to get this to work).

<br>

#### Restricting to Meaningful Cases
One work around I tried is restricting myself only those underlying/tenor combinations that had meaningful sharpes for all three delta variations.


**Delta-Hedge**
```{r, all_positive_dh, echo=FALSE, cache=TRUE}
# restricting only to underlying/tenor combinations
# with where all three delta variations have positive returns

# number of total cases
int_all_positive <-
    df_sharpe %>% filter(variation == 0.1) %>%
        left_join(
            df_sharpe %>% filter(variation == 0.3)
            , by = c("underlying", "tenor")
            , suffix = c("_10", "_30")
        ) %>%
        left_join(
            df_sharpe %>% filter(variation == 0.5)
            , by = c("underlying", "tenor")
            , suffix = c("", "_50")
        ) %>%
        rename(
            sharpe_naked_50 = sharpe_naked
            , sharpe_dh_50 = sharpe_dh
        ) %>% 
        filter(sharpe_dh_10 > 0) %>% 
        filter(sharpe_dh_30 > 0) %>% 
        filter(sharpe_dh_50 > 0) %>% 
        nrow()

# check cases where weekly is better
int_10_delta_best <-
    df_sharpe %>% filter(variation == 0.1) %>%
        left_join(
            df_sharpe %>% filter(variation == 0.3)
            , by = c("underlying", "tenor")
            , suffix = c("_10", "_30")
        ) %>%
        left_join(
            df_sharpe %>% filter(variation == 0.5)
            , by = c("underlying", "tenor")
            , suffix = c("", "_50")
        ) %>%
        rename(
            sharpe_naked_50 = sharpe_naked
            , sharpe_dh_50 = sharpe_dh
        ) %>% 
        filter(sharpe_dh_10 > 0) %>% 
        filter(sharpe_dh_30 > 0) %>% 
        filter(sharpe_dh_50 > 0) %>%
        filter(
            (sharpe_dh_10 >= sharpe_dh_30) &
            (sharpe_dh_10 >= sharpe_dh_50)
        ) %>% 
        nrow()

# printing results to screen
print(paste0("Count all positive (delta-hedge): ", int_all_positive))
print(paste0("Count 10-delta is best (delta-hedge): ", int_10_delta_best))
print(
    paste0(
        "Portion for which 10-delta is best (delta-hedge): "
        , round(int_10_delta_best / int_all_positive, 2)
    )
)
```
The delta-hedge percentage is 92%, which seems reasonable.

**Naked**
```{r, all_positive_naked, echo=FALSE, cache=TRUE}
# restricting only to underlying/tenor combinations
# with where all three delta variations have positive returns

# number of total cases
int_all_positive <-
    df_sharpe %>% filter(variation == 0.1) %>%
        left_join(
            df_sharpe %>% filter(variation == 0.3)
            , by = c("underlying", "tenor")
            , suffix = c("_10", "_30")
        ) %>%
        left_join(
            df_sharpe %>% filter(variation == 0.5)
            , by = c("underlying", "tenor")
            , suffix = c("", "_50")
        ) %>%
        rename(
            sharpe_naked_50 = sharpe_naked
            , sharpe_dh_50 = sharpe_dh
        ) %>% 
        filter(sharpe_naked_10 > 0) %>% 
        filter(sharpe_naked_30 > 0) %>% 
        filter(sharpe_naked_50 > 0) %>% 
        nrow()

# check cases where weekly is better
int_10_delta_best <-
    df_sharpe %>% filter(variation == 0.1) %>%
        left_join(
            df_sharpe %>% filter(variation == 0.3)
            , by = c("underlying", "tenor")
            , suffix = c("_10", "_30")
        ) %>%
        left_join(
            df_sharpe %>% filter(variation == 0.5)
            , by = c("underlying", "tenor")
            , suffix = c("", "_50")
        ) %>%
        rename(
            sharpe_naked_50 = sharpe_naked
            , sharpe_dh_50 = sharpe_dh
        ) %>% 
        filter(sharpe_naked_10 > 0) %>% 
        filter(sharpe_naked_30 > 0) %>% 
        filter(sharpe_naked_50 > 0) %>%
        filter(
            (sharpe_naked_10 >= sharpe_naked_30) &
            (sharpe_naked_10 >= sharpe_naked_50)
        ) %>% 
        nrow()

# printing results to screen
print(paste0("Count all positive (naked): ", int_all_positive))
print(paste0("Count 10-delta is best (naked): ", int_10_delta_best))
print(
    paste0(
        "Portion for which 10-delta is best (naked): "
        , round(int_10_delta_best / int_all_positive, 2)
    )
)
```
The naked percentage of 73% is a bit lower, but still in-line with expectiations.

<br>

#### Compare with Rank-Sharpe
I wasn't able to get the query to work with this - the results seemed totally out of wack.  However, I'm pretty confident with the other evidence in this analysis, as well as my previous experience, so I am going to stil with 10-delta strangles when trading.

I can revisit this approach if needed.

<!-- Another work around that I came up with is the concept of a rank-Sharpe, which is calculated by taking the rank of the avg-pnl and dividing by the rank of the stdev-pnl.  This worked well, and gave  the expected results. -->

<!-- For both naked and delta-hedge there are 36 underlying/variation combinations: 3 delta-variations and 12 underlyings. -->

<!-- ```{r, rank_sharpe_ratio_calc, include=FALSE, cache=TRUE} -->
<!-- df_rank_sharpe <- -->
<!--     df_sharpe %>% -->
<!--         mutate( -->
<!--             avg_naked_rank = rank(avg_naked) -->
<!--             , sd_naked_rank = rank(sd_naked) -->
<!--             , avg_dh_rank = rank(avg_dh) -->
<!--             , sd_dh_rank = rank(sd_dh) -->
<!--         ) %>% -->
<!--         mutate( -->
<!--             rank_sharpe_naked = avg_naked_rank / sd_naked_rank -->
<!--             , rank_sharpe_dh = avg_dh_rank / sd_dh_rank -->
<!--         ) -->

<!-- ``` -->

<!-- **Delta-Hedge** -->
<!-- ```{r, delta_hedge_sharpe_rank_test, echo=FALSE, cache=TRUE} -->
<!-- int_weekly_better <- -->
<!--     df_rank_sharpe %>% filter(tenor=="monthly") %>%  -->
<!--         left_join( -->
<!--             df_rank_sharpe %>% filter(tenor=="weekly") -->
<!--             , by = c("underlying_symbol", "variation") -->
<!--             , suffix = c("_monthly", "_weekly") -->
<!--         ) %>%  -->
<!--         filter( -->
<!--            rank_sharpe_dh_weekly > rank_sharpe_dh_monthly  -->
<!--         ) %>%  -->
<!--         nrow() -->


<!-- print( -->
<!--     paste0("weekly better than monthly (delta-hedge): ", int_weekly_better, " of 36.") -->
<!-- ) -->

<!-- print( -->
<!--     paste0("Percent (delta-hedge): ", round(int_weekly_better / 36, 2)) -->
<!-- ) -->
<!-- ``` -->

<!-- The delta-hedge percentage of 83% looks as expected. -->

<!-- **Naked:** -->
<!-- ```{r, naked_sharpe_rank_test, echo=FALSE} -->
<!-- int_weekly_better <- -->
<!--         df_rank_sharpe %>% filter(tenor=="monthly") %>%  -->
<!--         left_join( -->
<!--             df_rank_sharpe %>% filter(tenor=="weekly") -->
<!--             , by = c("underlying_symbol", "variation") -->
<!--             , suffix = c("_monthly", "_weekly") -->
<!--         ) %>%  -->
<!--         filter( -->
<!--            rank_sharpe_naked_weekly > rank_sharpe_naked_monthly  -->
<!--         ) %>%  -->
<!--         nrow() -->


<!-- print( -->
<!--     paste0("weekly better than monthly (naked): ", int_weekly_better, " of 36.") -->
<!-- ) -->

<!-- print( -->
<!--     paste0("Percent (naked): ", round(int_weekly_better / 36, 2)) -->
<!-- ) -->
<!-- ``` -->

<!-- The naked percentage of 92% looks as googd also. -->


<br>


### Sharpe Ratio All Underlyings Combined
In this section we aggregate all the underlyings together for each tenor/delta-variation combination, and then calculate the sharpe ratios for the weekly and monthly strategies.

<br>

```{r, graph_sharpe_ratio_underlyings_combined_dh, echo=FALSE, cache=TRUE, fig.height=3, fig.width=7.5}
df_pnl %>%
    group_by(tenor, variation, data_date) %>%
    summarize(
            naked = sum(scaled_dly_opt_pnl)
            , dh = sum(scaled_dly_tot_pnl)
        )  %>%
    group_by(tenor, variation) %>%
    summarize(
        avg_naked = mean(naked)
        , avg_dh = mean(dh)
        , sd_naked = sd(naked)
        , sd_dh = sd(dh)
        , sharpe_naked = (mean(naked) / sd(naked)) * sqrt(252)
        , sharpe_dh = (mean(dh) / sd(dh)) * sqrt(252)

    ) %>%
    ggplot(aes(x = tenor, y = sharpe_dh, fill=tenor)) +
    geom_bar(stat = "identity", position = "dodge")  +
    geom_text(aes(label=round(sharpe_dh, 2), vjust=-0.25)) +
    facet_wrap(~factor(variation)) +
    ylim(-.25, 1.4) +
    labs(
        title = "Delta-Hedge: Sharpe All Underlying Combined"
        , subtitle = "Monthy vs Weekly"
        , x = "delta-variation"
        , y = "sharpe-ratio"
    )
```




```{r, graph_sharpe_ratio_underlyings_combined_naked, echo=FALSE,fig.height=3, fig.width=7.5, cache=TRUE}
df_pnl %>%
    group_by(tenor, variation, data_date) %>%
    summarize(
            naked = sum(scaled_dly_opt_pnl)
            , dh = sum(scaled_dly_tot_pnl)
        )  %>%
    group_by(tenor, variation) %>%
    summarize(
        avg_naked = mean(naked)
        , avg_dh = mean(dh)
        , sd_naked = sd(naked)
        , sd_dh = sd(dh)
        , sharpe_naked = (mean(naked) / sd(naked)) * sqrt(252)
        , sharpe_dh = (mean(dh) / sd(dh)) * sqrt(252)

    ) %>%
    ggplot(aes(x = tenor, y = sharpe_naked, fill=tenor)) +
    geom_bar(stat = "identity", position = "dodge")  +
    geom_text(aes(label=round(sharpe_naked, 2), vjust=-0.25)) +
    facet_wrap(~factor(variation)) +
    ylim(-0.25 , 1.4) +
    labs(
        title = "Naked: Sharpe All Underlyings Combined"
        , subtitle = "Monthy vs Weekly"
        , x = "delta-variation"
        , y = "sharpe-ratio"
    )
```

<br>

For delta-hedge, both tenors demonstrate the result.  For naked options: in the monthly tenor, the 10-delta is the only one with positive returns; in the weekly tenor, 10-delta outperforms 30-delta in terms of sharpe, and the 50-delta had negative returns.

<br>

### Conclusion

Trade 10-delta strangles until you have evidence to the contrary.


















